\documentclass{cv}
\usepackage{hyperref}

\usepackage[left=0.40in,top=1.0in,right=0.40in,bottom=1.0in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{natbib, bibentry}
\usepackage{fancyhdr}
\setlength{\headheight}{13.59999pt}
\pagestyle{fancy}
\lhead{\textit{Resume - Computer Science Ph.D.}}
\rhead{Deyuan (Mike) He}
% \chead{\href{mailto:dh63@cs.washington.edu}{dh63@cs.washington.edu}}
\titlespacing*{\rSection}{0pt}{1.1\baselineskip}{\baselineskip}
\newcommand{\myul}[2][blue]{\setulcolor{#1}\ul{#2}\setulcolor{blue}}
\usepackage{xcolor,soul,lipsum}
\begin{document}
\vspace{-0.5in}
\bibliographystyle{unsrt}
\nobibliography{publication.bib}
\MakeUppercase{\Large{\textbf{Mike He}}} \hfill {\em{\href{mailto:dh63@cs.washington.edu}{dh63@cs.washington.edu}}}\\
\vspace{-5pt}\href{https://ad1024.github.io}{https://ad1024.github.io} \hfill{\em (206)~$\cdot$~887~$\cdot$~8588}


%----------------------------------------------------------------------------------------
%	Specifications
%----------------------------------------------------------------------------------------

	% \begin{rSection}{Skills}
	% 	\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }
	% 		Languages & C/C++, Python, Java, Rust, OCaml, Haskell, Coq, Agda, \LaTeX \\
	% 		Skills    & Certified \& Functional Programming, Automated Verification \\
	% 		Others    & I've been playing the violin for 17 years. I like Symphonies composed by \href{https://imslp.org/wiki/Category:Mahler,_Gustav}{Gustav Mahler}.
	% 	\end{tabular}
	% \end{rSection}
	% \vspace{-5pt}
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

	\begin{rSection}{Education}
	{\bf University of Washington, Seattle} \hfill {\em Sept. 2018---Est. Jun. 2022} \\
	\textit{B.S. in Computer Science}
	\vspace{-5pt}
        \begin{itemize}[leftmargin=*]
            \setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
			\setlength{\parsep}{0pt}
			\item Major GPA: 3.79 / 4.00
            \item Fields of Study: Programming Languages \& Formal Verification \& Compilers \& MLSys
            \item Honors: Dean's List (College of Art \& Science) 2018--Now; CRA Outstanding Undergraduate Researcher Award nominee of the Allen School (2021)
		\end{itemize}
	\end{rSection}
	\vspace{-5pt}
    \begin{rSection}{Publications}
		\begin{enumerate}
			\setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
			\setlength{\parsep}{0pt}
			\item \bibentry{kirisame2021dynamic} (\small{*: Equal Contribution})
			\item \textbf{(Under review at PLDI '22)} \bibentry{pldi22}
		\end{enumerate}
        \vspace{-5pt}
	\end{rSection}
	\vspace{1pt}
	\begin{rSection}{Workshop Papers}
		\begin{enumerate}
			\item \bibentry{latte21} (\small{*: Equal Contribution})
		\end{enumerate}
	\end{rSection}
    \vspace{1pt}

    \begin{rSection}{Experience}
        \begin{rSubsection}{3LA, LATTE '21}{June. 2020---Now}{Research Assistant @ PLSE}{Seattle, WA}
            \item \href{https://capra.cs.cornell.edu/latte21/paper/30.pdf}{\color{blue} \myul{3LA}} proposes an end-to-end compilation flow that provides \textbf{flexible} and \textbf{verifiable} compiler support for custom Deep Learning (\textbf{DL}) accelerators. 3LA has a builtin implementation agnostic pattern matching algorithm that is capable of find accelerator supported workloads in DL models leveraging the power of Equality Saturation. Moreover, 3LA addresses the mapping gap between DL models represented in high-level domain-specific languages (DSLs) and specialized accelerators using Instruction-level Abstraction (\textbf{ILA}) as the software-hardware interface.
            \item Co-authored a Workshop paper and a conference paper (under review at PLDI)
            \item Designed and led the implementation of Flexible Matching algorithm to match supported workloads
            \item \textbf{Talks \& Presentations}:
                \begin{enumerate}
					\setlength{\itemsep}{1pt}
					\setlength{\parskip}{0pt}
					\setlength{\parsep}{0pt}
                    \item \textit{From DSLs to Accelerator-rich Platform: Addressing the Mapping Gap}, Sept. 2021 at Intel (presented jointly with \href{https://homes.cs.washington.edu/~sslyu/}{\color{blue} \myul {Steven Lyubomirsky}})
                    \item \textit{Correct \& Flexible Compiler Support for Custom Accelerators}, Sept. 2021 at SRC ADA Center
                \end{enumerate} 
        \end{rSubsection}

        \begin{rSubsection}{Dynamic Tensor Rematerialization, ICLR '21}{Oct. 2019---Aug. 2021}{Research Assistant @ PLSE}{Seattle, WA}
            \item \href{https://github.com/uwsampl/dtr-prototype}{\color{blue} \myul{Dynamic Tensor Rematerialization}} (\textbf{DTR}) is a greedy gradient checkpointing algorithm. DTR \textbf{enables} training Deep Learning models on memory-constrained devices. Unlike previous approaches, DTR does not need any information of the DL model architectures ahead-of-time; instead it saves memory by evicting and recomputing tensors \textbf{on the fly}, i.e. trading time for memory, which further exploit opportunities of using gradient checkpointing on DL trainings. DTR is comparably efficient as previous approaches: it requires only $\mathcal{O}(N)$ more forward computations when training a $N$-layer linear feed-forward neural network with an $\Omega(\sqrt{N})$ memory budget.
            \item Co-authored a paper accepted at ICLR'21 Spotlight track
			\item Developed and improved the evaluation infrastructure of the prototype implementation in PyTorch
        \end{rSubsection}

		\begin{rSubsection}{Paul G. Allen School, University of Washington}{Mar. 2021---June. 2021}{Teaching Assistant}{Seattle, WA}
			\item Worked as a TA for \textbf{Principles of Programming Languages} (CSE 505)
			\item Helped re-designing CSE 505 and developing course materials for various topics about PL and formal verification (\textbf{Hoare Logic}, \textbf{Lambda Calculus} and \textbf{System F}, etc.) in \textbf{Coq}.
		\end{rSubsection}
    \end{rSection}

	\begin{rSection}{Service}
    	\begin{enumerate}
    		\setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
    		\setlength{\parsep}{0pt}
    		\item[$\rightarrow$] \textbf{MICRO '21}, Artifact Evaluation
    	\end{enumerate}
	\end{rSection}

	\begin{rSection}{Projects}

		%------------------------------
		%      veripy
		%------------------------------
		\textbf{\href{https://github.com/AD1024/veripy}{\color{blue} \myul{veripy}}} % \hfill {\em {\href{https://github.com/AD1024/veripy}{On GitHub}}}
		\vspace{-5pt}

		\begin{itemize}
			\setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
			\setlength{\parsep}{0pt}
			\item An easy-to-use auto-active program verification library for Python programs written in \textbf{Python}.
			\item The library is shallowly embedded in Python and the interface is implemented as \textbf{decorators}. It compiles annotated Python functions to \textbf{SMT} formulae and calls \textbf{SMT solver} to check whether it matches the given specification and gives a counter-example input when it violates any constraint.
			% \item \textbf{Language} \& \textsc{Tools}: \textbf{Python 3}, \textbf{SMT-LIB}, \textsc{Z3}, \textsc{pyparsing}
			% \item Keywords: SMT Solver, Static Analysis, Hoare Logic, Program Verification
		\end{itemize}

		%------------------------------
		%      dtlc
		%------------------------------
		\textbf{\href{https://github.com/AD1024/dtlc}{\color{blue} \myul{dtlc}}} % \hfill {\em {\href{https://github.com/AD1024/dtlc}{On GitHub}}}
		\vspace{-5pt}

		\begin{itemize}
			\setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
			\setlength{\parsep}{0pt}
			\item Implemented \textbf{dependently-typed} lambda calculus in Martin-Löf style intuitionistic type theory.
			\item Written in \textbf{OCaml}, \textbf{dtlc} has a language frontend \textbf{Lexer \& Parser} implemented using \textbf{Menhir}. Core language supports \textbf{type unification} with \textbf{metavariables} which makes the type inference stronger.
			\item Implemented eliminators for \textbf{naturals}, \textbf{identity type}, \textbf{union type}, etc.
			% \item \textbf{Language} \& \textsc{Tools}: \textbf{OCaml}, \textsc{Menhir}, \textsc{Dune}
			% \item Keywords: Type Theory - Dependent Type, Proof Assistant, Functional Programming
		\end{itemize}

		\textbf{\href{https://github.com/AD1024/Sager}{\color{blue} \myul{Sager}}} % \hfill {\em {\href{https://github.com/AD1024/Sager}{On GitHub}}}
		\begin{itemize}
			\setlength{\itemsep}{1pt}
            \setlength{\parskip}{0pt}
			\setlength{\parsep}{0pt}
			\item Course project of CSE 507 - Computer-aided Reasoning for Software
			\item A demonic data structure synthesizer written in \textsc{rosette}, a \textbf{solver-aided} language based on \textbf{Racket}.
			\item \textbf{Sager} is able to exploit algorithm bottleneck by performing \textbf{symbolic exeuction} over the whole algorithm and using \textbf{SMT solver} to synthesize a sample data structure the algorithm works on that pushes the algorithm to its worst-case performance.
		\end{itemize}
	\end{rSection}
\end{document}
